### 2009-04-17 docs/runtime_parameters/runtime_parameters.tex
changed "radius" in _parameters to "rotation_radius" so we don't confuse with the many local radius we declare throughout the code

\verb=  job_name  = &    &  "" \\

@@

\verb=  min_eff  = &    &  0.7d0 \\

@@

\verb=  radius  = &    &  1.0e6\_dp\_t \\
\verb=  ref_ratio  = &    &  2 \\
\verb=  regrid_int  = &    &  -1 \\

@@

\verb=  rotational_frequency  = &    &  ZERO \\

@@

\verb=  slope_order  = &    &  4 \\

@@

\verb=  use_delta_gamma1_term  = &    &  .false. \\

@@

\verb=  use_etarho  = &    &  .true. \\

>>>>

\verb=  job_name  = &   job name printed in output  &  "" \\

@@

\verb=  min_eff  = &   parameter for cluster algorithm for making new grids in adaptive problems  &  0.7d0 \\

@@

\verb=  ref_ratio  = &   Refinement ratio for multilevel problems  &  2 \\
\verb=  regrid_int  = &   How often we regrid.  &  -1 \\

@@

\verb=  rotation_radius  = &   radius used for computing centrifugal term in rotation problems  &  1.0e6\_dp\_t \\
\verb=  rotational_frequency  = &   rotational frequency used for computing centrifugal term in rotation problems.  &  ZERO \\

@@

\verb=  slope_order  = &   order of slopes in Godunov algorithm.  Options are 0, 2, or 4.  &  4 \\

@@

\verb=  use_delta_gamma1_term  = &   turns on second order correction to delta gamma1 term  &  .false. \\

@@

\verb=  use_etarho  = &   turn on the etarho term as described in flow chart  &  .true. \\
